Address Reuse in the Bitcoin Network

### 2014-01-08 paper.tex
included plot and stats in paper

However, keeping the addresses completely anonymous is not always possible.
In the simplest example in which Bob wants to receive a payment from Alice, he has to generate an address and hand it to Alice.
At that point, Alice knows that that particular address, in our previous example \texttt{1U8yx} belongs to Bob.
Then Alice can monitor the Blockchain for transactions involving

Imagine that Ann wants to send another bitcoin to Bob.
Ann can either send the new bitcoin to the same address \texttt{1U8yx} that she used before, or can ask Bob to generate a new address.
In the first case, the address \texttt{1U8yx} is being re-used and in the second, address re-use is avoided.

>>>>

\section{Evidence of Address Re-use in the Blockchain}

We use Obelisk and Libbitcoin to download and query the blockchain.
We count how many times each address appears as the output of a transaction.

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Address re-use Statistics}
\label{table_example}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{|cc|}
\hline
Mean & 3.18\\
Min & 1\\
25th perc. & 1 \\
50th perc. & 1 \\
75th perc. & 1 \\
Max & 1,238,931\\
Number of addresses & 12,963,199 \\
Number of uses & 41,244,997 \\
Addresses used once & 10,476,899 \\
Addressed used twice & 1,397,373\\
Used over 100 times & 25,004 \\
\hline
\end{tabular}
\end{table}

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{figures/address-reuse.eps}
\caption{Number of addresses for re-use factor from 1 to 100. Note the log scale.}
\label{fig:address-reuse}
\end{figure}
